% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2012 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt, letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[sc]{mathpazo}
\usepackage{enumitem}
%\usepackage{enumerate}

% Set your name here
\def\name{Suli Yang}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body = {6.5in, 9.1in},
  left = 1.0in,
  top = 1.0in,
}

% no page ordering
\pagenumbering{gobble}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large}
\subsectionfont{\rmfamily\mdseries\normalsize}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.2em}
    \setlength{\itemsep}{0.12em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.12em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

\bigskip

%\begin{minipage}{0.45\linewidth}
%\hypersetup{urlcolor=black}
%\href{http://www.wisc.edu}{University of Wisconsin -- Madison}\\
%\href{http://www.cs.wisc.edu}{Department of Computer Sciences}\\
%7354, 1210 W. Dayton St., WI, 53706
%Building 13, Youjiadu, Wenjiang District
%Chengdu, Sichuan, China, 611130
%\end{minipage}
\begin{minipage}{0.45\linewidth}
\hypersetup{urlcolor=black}
\begin{tabular}{ll}
  Phone: & (+86) 136-9904-9416\\
  Email: & \href{mailto:suli@cs.wisc.edu}{\tt suli@cs.wisc.edu}\\
  Email: & \href{mailto:yangsuli@gmail.com}{\tt yangsuli@gmail.com}\\
  Homepage: & \href{http://pages.cs.wisc.edu/~suli}
  	{\tt http://pages.cs.wisc.edu/$\sim$suli}
\end{tabular}
\end{minipage}

\section*{\textsc{Research Interests}}

Resilience, Manageability, and Performance of Storage Systems and Data Management Systems.
Software-Defined Storage and Networking Systems.

\if 0
\vspace{0.15cm}
\noindent
{\textit{Research Summary:}} 
    My research builds high-performance and scalable distributed storage systems from the bottom up. 
    In today`’s datacenter, the presence of performant yet heterogeneous devices (e.g., NVMe, NVM, NVMe-oF, RDMA, etc.) further increases the complexity to scale distributed storage systems and deliver high performance. My work aims to design layered distributed storage systems where each layer will scale independently to each other with optimized performance and parallelism within the layer, starting from local file system up to the geo-distributed setting. 
    
\fi


\section*{\textsc{Education}}
\begin{itemize}
  \item {\bf Department of Computer Sciences, University of Wisconsin -- Madison}\hfill 2011 --  2017\\
    Ph.D. in Computer Science, with a focus on file systems and storage systems\\
    Thesis: {\it Principled Schedulability in Local and Distributed Storage Systems}\\
    Advisors: { Prof. Andrea Arpaci-Dusseau \& Prof. Remzi Arpaci-Dusseau}%\\

  \item {\bf Department of Physics, University of Wisconsin -- Madison}\hfill 2009 -- 2011\\
    M.A. in Physics %\\

  \item {\bf Department of Physics, Peking University}\hfill 2004 -- 2009\\
    B.S. in Physics
    % Thesis: {\it Depth-aware layered edge for elastic RGB-D object proposal}
    % (Awarded Excellent in Province)
\end{itemize}

\section*{\textsc{Work Experience}}

\begin{itemize}

\item {\bf Ant Financial Service Group}, Hangzhou, China \hfill 2018 -- 2021\\
{\it Software Engineer} %\\ %Mentor: Dr. Marc De Kruijf

\item {\bf NetApp Inc.}, Sunnyvale, USA \hfill 2013 -- 2015\\
{\it Research Intern} \\ Mentor: Kiran Srinivasan

\item {\bf Intuit Inc.}, Montain View, USA \hfill Summer 2011\\
{\it Software Engineering Intern} %\\%Class: Advanced Operating System. Instructor: Prof. Andrea Arpaci-Dusseau

\item {\bf CERN Laboratory for Particle Physics}, Geneva, Switzerland
  \hfill 2009 -- 2010\\
{\it Research Intern} \\Advisor: Sau Lan Wu

\item {\bf Deutsches Elektronen-Synchrotron (DESY)}, Berlin, Germany\hfill Summar 2008\\
{\it Research Intern} \\Mentor: Ishmael Valdez
 %\\Class: Computer Operating System. Instructors: Prof. Bin Luo \& Prof. Jidong Ge
\end{itemize}



%\section*{\textsc{Refereed Conference Publications}}
\section*{\textsc{Peer-Reviewed Conference Publications}}

\begin{enumerate}[fullwidth,itemindent=1.1em,label={[\arabic*]}]

  %TODO: Aishywa's publication seems nice, where she listed conference abbreviastion in a separate column. See if I can do it?  http://pages.cs.wisc.edu/~ag/pdf/cv.pdf

	\item {\bf Suli Yang}, Jing Liu, Andrea C. Arpaci-Dusseau, and Remzi H. Arpaci-Dusseau. \textit{Principled Schedulability Analysis for Distributed Storage Systems using Thread Architecture Models.}
        In Proceedings of the 13th Symposium on Operating System and Design Implementation (OSDI '18), CA, USA, 2018.

        \item Al-Kiswany, Samer, {\bf Suli Yang}, Andrea C. Arpaci-Dusseau, and Remzi H. Arpaci-Dusseau. \textit{NICE: Network-Integrated Cluster-Efficient Storage.}  
        In Proceedings of the 26th International Symposium on High-Performance Parallel and Distributed Computing (HPDC '17), Washington D.C., USA, 2017.

        \item {\bf Suli Yang}, Kiran Srinivasan, Kishore Udayashankar, Swetha Krishnan, Jingxin Feng, Yupu Zhang, Andrea C. Arpaci-Dusseau, and Remzi H. Arpaci-Dusseau. \textit{Tombolo: Performance Enhancements for Cloud Storage Gateways.} 
         In 2016 32nd Symposium on Mass Storage Systems and Technologies (MSST '16), Santa Clara, CA, USA, 2016.

         \item {\bf Suli Yang}, Tyler Harter, Nishant Agrawal, Salini Selvaraj Kowsalya, Anand Krishnamurthy, Samer Al-Kiswany, Rini T. Kaushik, Andrea C. Arpaci-Dusseau, and Remzi H. Arpaci-Dusseau. \textit{Split-Level I/O Scheduling.} 
         In Proceedings of the 25th Symposium on Operating Systems Principles (SOSP '15), Monterey, CA, USA, 2015.

         \item Grandl, Robert, Yizheng Chen, Junaid Khalid, {\bf Suli Yang}, Ashok Anand, Theophilus Benson, and Aditya Akella. \textit{Harmony: Coordinating Network, Compute, and Storage in Software-Defined Clouds.}
          In Proceedings of the 4th annual Symposium on Cloud Computing (SOCC '13), Santa Clara, CA, USA, 2013.

\end{enumerate}


%\section*{\textsc{Journal and Workshops}}
\section*{\textsc{Peer-Reviewed Journal and Workshop Publications}}

\begin{enumerate}[fullwidth,itemindent=1em,label={[\arabic*]}]
      \item Kettaneh, Ibrahim, Ahmed Alquraan, Hatem Takruri, {\bf Suli Yang}, Andrea C. Arpaci-Dusseau, Remzi H. Arpaci-Dusseau, and Samer Al-Kiswany. \textit{The Network-Integrated Storage System.} 
      IEEE Transactions on Parallel and Distributed Systems (TPDS) 31, no. 2 (2019): 486-500.
      %TODO: may need to format the journal publication a bit better? No page info? 31(2), 2019? See aishywa's CV

       \item Lee, Eunji, Youil Han, {\bf Suli Yang}, Andrea C. Arpaci-Dusseau, and Remzi H. Arpaci-Dusseau. \textit{How to Teach an Old File System Dog New Object Store Tricks.} 
        In 10th {USENIX} Workshop on Hot Topics in Storage and File Systems (HotStorage '18), Boston, MA, USA 2018.
	
\end{enumerate}

\if 0
\section*{\textsc{Honors and Awards}}
\begin{itemize}
  \item Travel Grant (OSDI-18), USENIX \hfill 2018
  \item Student Scholarship (SOSP-17), SIGOPS \hfill 2017
  \item CS Summer Research Award, UW-Madison \hfill 2017
  \item Graduate Research Fellowship, UW-Madison \hfill 2016 -- 2017
  \item Outstanding Graduate, Nanjing University\hfill 2016
  \item Departmental Best Undergraduate Thesis, University Highest Honor \hfill 2016
  \item Outstanding National Undergraduate Innovation Project (Role: Lead, Grant: $\sim$3000\$)  \hfill 2016
  \item National Encouraging Scholarship, Ministry of Education of China \hfill 2014, 2015
  \item National Scholarship, Ministry of Education of China \hfill 2013
\end{itemize}
\fi

\section*{\textsc{Patents}}
\begin{enumerate}[fullwidth,itemindent=1.1em,label={[\arabic*]}]
    \item Zhenkun Yang and {\bf Suli Yang}. \textit{Data Writing Method, Device and Equipment.} C.N. Patent 111,399,780, issued August 24, 2021
    %link: https://patents.google.com/patent/CN111399780A/en?oq=CN111399780A

     \item {\bf Suli Yang}, Kishore Kasi Udayashankar, Jingxin Feng, Swetha Krishnan, and Kiran Srinivasan. \textit{Methods for Combining Access History and Sequentiality for Intelligent Prefetching and Devices thereof.} U.S. Patent 9,471,497, issued October 18, 2016.

\end{enumerate}

%TODO: make have a coverage on research section, just as Aishwarya's CV?

\section*{\textsc{Service}}
\begin{itemize}
	\item ACM Transactions on Storage (TOS), Reviewer \hfill 2021
	\item IEEE's Transactions on Cloud Computing (TCC), Reviewer \hfill 2021
        \item IEEE's Transactions on Parallel and Distributed Systems (TPDS), Reviewer \hfill 2021
	\item Computers \& Security (COSE), Reviewer \hfill 2021
\end{itemize}

\section*{\textsc{Presentations and Invited Talks}}
\begin{itemize}
       \item {\bf{Principled Schedulability Analysis for Distributed Storage Systems using Thread Architecture Models.}} \\
        %{\small{Talk at OSDI '18, Carlsbad, CA.}} \hfill Oct. 2018
        {\small{Talk at OSDI '18}} \hfill Oct. 2018

       \item {\bf{Tombolo: Performance Enhancements for Cloud Storage Gateways.}} \\
        %{\small{Talk at MSST '16, Santa Clara, CA.}}  \hfill Jun. 2016
        {\small{Talk at MSST '16}}  \hfill Jun. 2016
       
       \item {\bf{Split-Level I/O Scheduling.}} \\
        %{\small{Talk at SOSP '15, Monterey, CA.}}  \hfill Oct. 2015\\
        {\small{Talk at SOSP '15}}  \hfill Oct. 2015\\
	{\small{Invited talk at Tintri Inc.}}	   \hfill Jul. 2015
\end{itemize}

%\medskip
%\begin{center}
%  \begin{small}
%  Last updated: \today
%  \end{small}
%\end{center}
\end{document}
